Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-22 graph_housing_exp2_distr_3_5.tex
Change all plots from probability to probability density

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=$C$,
			ylabel=$E$,
			colorbar,
			point meta min=0, point meta max=0.5,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.05,...,0.51},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.3850,0.1105) (3.8750,0.3850,0.1105) (3.8750,0.4460,0.1105) (0.4600,0.4460,0.1105)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4460,0.0000) (3.8750,0.4460,0.0000) (3.8750,0.4485,0.0000) (0.4600,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4485,0.0000) (3.8750,0.4485,0.0000) (3.8750,0.4555,0.0000) (0.4600,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4555,0.0130) (3.8750,0.4555,0.0130) (3.8750,0.4620,0.0130) (0.4600,0.4620,0.0130)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4620,0.0000) (3.8750,0.4620,0.0000) (3.8750,0.4705,0.0000) (0.4600,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4705,0.0285) (3.8750,0.4705,0.0285) (3.8750,0.4910,0.0285) (0.4600,0.4910,0.0285)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4910,0.0000) (3.8750,0.4910,0.0000) (3.8750,0.4960,0.0000) (0.4600,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4960,0.0000) (3.8750,0.4960,0.0000) (3.8750,0.5015,0.0000) (0.4600,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5015,0.0000) (3.8750,0.5015,0.0000) (3.8750,0.5085,0.0000) (0.4600,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5085,0.0000) (3.8750,0.5085,0.0000) (3.8750,0.5165,0.0000) (0.4600,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5165,0.0025) (3.8750,0.5165,0.0025) (3.8750,0.5410,0.0025) (0.4600,0.5410,0.0025)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5410,0.0000) (3.8750,0.5410,0.0000) (3.8750,0.5485,0.0000) (0.4600,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5485,0.0000) (3.8750,0.5485,0.0000) (3.8750,0.5775,0.0000) (0.4600,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5775,0.0000) (3.8750,0.5775,0.0000) (3.8750,0.6010,0.0000) (0.4600,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6010,0.0000) (3.8750,0.6010,0.0000) (3.8750,0.6070,0.0000) (0.4600,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6070,0.0000) (3.8750,0.6070,0.0000) (3.8750,0.6115,0.0000) (0.4600,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6115,0.0000) (3.8750,0.6115,0.0000) (3.8750,0.6190,0.0000) (0.4600,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6190,0.0000) (3.8750,0.6190,0.0000) (3.8750,0.6275,0.0000) (0.4600,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6275,0.0000) (3.8750,0.6275,0.0000) (3.8750,0.6390,0.0000) (0.4600,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6390,0.0000) (3.8750,0.6390,0.0000) (3.8750,0.6510,0.0000) (0.4600,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6510,0.0000) (3.8750,0.6510,0.0000) (3.8750,0.8205,0.0000) (0.4600,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.8205,0.0000) (3.8750,0.8205,0.0000) (3.8750,0.8710,0.0000) (0.4600,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.3850,0.0000) (3.9850,0.3850,0.0000) (3.9850,0.4460,0.0000) (3.8750,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4460,0.0000) (3.9850,0.4460,0.0000) (3.9850,0.4485,0.0000) (3.8750,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4485,0.0000) (3.9850,0.4485,0.0000) (3.9850,0.4555,0.0000) (3.8750,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4555,0.0000) (3.9850,0.4555,0.0000) (3.9850,0.4620,0.0000) (3.8750,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4620,0.0000) (3.9850,0.4620,0.0000) (3.9850,0.4705,0.0000) (3.8750,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4705,0.0000) (3.9850,0.4705,0.0000) (3.9850,0.4910,0.0000) (3.8750,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4910,0.0000) (3.9850,0.4910,0.0000) (3.9850,0.4960,0.0000) (3.8750,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4960,0.0000) (3.9850,0.4960,0.0000) (3.9850,0.5015,0.0000) (3.8750,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5015,0.0000) (3.9850,0.5015,0.0000) (3.9850,0.5085,0.0000) (3.8750,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5085,0.0000) (3.9850,0.5085,0.0000) (3.9850,0.5165,0.0000) (3.8750,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5165,0.0000) (3.9850,0.5165,0.0000) (3.9850,0.5410,0.0000) (3.8750,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5410,0.0000) (3.9850,0.5410,0.0000) (3.9850,0.5485,0.0000) (3.8750,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5485,0.0035) (3.9850,0.5485,0.0035) (3.9850,0.5775,0.0035) (3.8750,0.5775,0.0035)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5775,0.0000) (3.9850,0.5775,0.0000) (3.9850,0.6010,0.0000) (3.8750,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6010,0.0000) (3.9850,0.6010,0.0000) (3.9850,0.6070,0.0000) (3.8750,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6070,0.0000) (3.9850,0.6070,0.0000) (3.9850,0.6115,0.0000) (3.8750,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6115,0.0000) (3.9850,0.6115,0.0000) (3.9850,0.6190,0.0000) (3.8750,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6190,0.0000) (3.9850,0.6190,0.0000) (3.9850,0.6275,0.0000) (3.8750,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6275,0.0000) (3.9850,0.6275,0.0000) (3.9850,0.6390,0.0000) (3.8750,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6390,0.0225) (3.9850,0.6390,0.0225) (3.9850,0.6510,0.0225) (3.8750,0.6510,0.0225)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6510,0.0000) (3.9850,0.6510,0.0000) (3.9850,0.8205,0.0000) (3.8750,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.8205,0.0000) (3.9850,0.8205,0.0000) (3.9850,0.8710,0.0000) (3.8750,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.3850,0.0680) (6.1450,0.3850,0.0680) (6.1450,0.4460,0.0680) (3.9850,0.4460,0.0680)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4460,0.0000) (6.1450,0.4460,0.0000) (6.1450,0.4485,0.0000) (3.9850,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4485,0.0210) (6.1450,0.4485,0.0210) (6.1450,0.4555,0.0210) (3.9850,0.4555,0.0210)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4555,0.0000) (6.1450,0.4555,0.0000) (6.1450,0.4620,0.0000) (3.9850,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4620,0.0000) (6.1450,0.4620,0.0000) (6.1450,0.4705,0.0000) (3.9850,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4705,0.0000) (6.1450,0.4705,0.0000) (6.1450,0.4910,0.0000) (3.9850,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4910,0.0000) (6.1450,0.4910,0.0000) (6.1450,0.4960,0.0000) (3.9850,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4960,0.0095) (6.1450,0.4960,0.0095) (6.1450,0.5015,0.0095) (3.9850,0.5015,0.0095)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5015,0.0000) (6.1450,0.5015,0.0000) (6.1450,0.5085,0.0000) (3.9850,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5085,0.0300) (6.1450,0.5085,0.0300) (6.1450,0.5165,0.0300) (3.9850,0.5165,0.0300)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5165,0.0000) (6.1450,0.5165,0.0000) (6.1450,0.5410,0.0000) (3.9850,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5410,0.0000) (6.1450,0.5410,0.0000) (6.1450,0.5485,0.0000) (3.9850,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5485,0.0000) (6.1450,0.5485,0.0000) (6.1450,0.5775,0.0000) (3.9850,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5775,0.0000) (6.1450,0.5775,0.0000) (6.1450,0.6010,0.0000) (3.9850,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6010,0.0000) (6.1450,0.6010,0.0000) (6.1450,0.6070,0.0000) (3.9850,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6070,0.0000) (6.1450,0.6070,0.0000) (6.1450,0.6115,0.0000) (3.9850,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6115,0.0000) (6.1450,0.6115,0.0000) (6.1450,0.6190,0.0000) (3.9850,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6190,0.0000) (6.1450,0.6190,0.0000) (6.1450,0.6275,0.0000) (3.9850,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6275,0.0000) (6.1450,0.6275,0.0000) (6.1450,0.6390,0.0000) (3.9850,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6390,0.0000) (6.1450,0.6390,0.0000) (6.1450,0.6510,0.0000) (3.9850,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6510,0.0000) (6.1450,0.6510,0.0000) (6.1450,0.8205,0.0000) (3.9850,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.8205,0.0000) (6.1450,0.8205,0.0000) (6.1450,0.8710,0.0000) (3.9850,0.8710,0.0000)};

>>>>

\begin{tikzpicture}
		\begin{axis}[
			view={0}{90},
			enlargelimits=0,
			zmin=0.0, zmax=1.0,
			xlabel=C,
			ylabel=E,
			colorbar,
			point meta min=0, point meta max=1.2,
			colormap={}{ gray(0cm)=(1); gray(1cm)=(0);},
			colorbar style={
			        ytick={0,0.24,...,1.3},
			        ylabel={probability density$ \times 10^{-1}$},
			        y label style={at={(axis description cs:6.5,0.5)},rotate=180,anchor=north},
			        yticklabel style={
			            text width=2.5em,
			            align=right,
			            /pgf/number format/.cd,
			                fixed,
			                fixed zerofill
			        }
			    }
			]

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.3850,0.053045) (3.8750,0.3850,0.053045) (3.8750,0.4460,0.0530) (0.4600,0.4460,0.0530)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4460,0.000000) (3.8750,0.4460,0.000000) (3.8750,0.4485,0.0000) (0.4600,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4485,0.000000) (3.8750,0.4485,0.000000) (3.8750,0.4555,0.0000) (0.4600,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4555,0.058565) (3.8750,0.4555,0.058565) (3.8750,0.4620,0.0586) (0.4600,0.4620,0.0586)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4620,0.000000) (3.8750,0.4620,0.000000) (3.8750,0.4705,0.0000) (0.4600,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4705,0.040710) (3.8750,0.4705,0.040710) (3.8750,0.4910,0.0407) (0.4600,0.4910,0.0407)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4910,0.000000) (3.8750,0.4910,0.000000) (3.8750,0.4960,0.0000) (0.4600,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.4960,0.000000) (3.8750,0.4960,0.000000) (3.8750,0.5015,0.0000) (0.4600,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5015,0.000000) (3.8750,0.5015,0.000000) (3.8750,0.5085,0.0000) (0.4600,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5085,0.000000) (3.8750,0.5085,0.000000) (3.8750,0.5165,0.0000) (0.4600,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5165,0.002988) (3.8750,0.5165,0.002988) (3.8750,0.5410,0.0030) (0.4600,0.5410,0.0030)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5410,0.000000) (3.8750,0.5410,0.000000) (3.8750,0.5485,0.0000) (0.4600,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5485,0.000000) (3.8750,0.5485,0.000000) (3.8750,0.5775,0.0000) (0.4600,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.5775,0.000000) (3.8750,0.5775,0.000000) (3.8750,0.6010,0.0000) (0.4600,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6010,0.000000) (3.8750,0.6010,0.000000) (3.8750,0.6070,0.0000) (0.4600,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6070,0.000000) (3.8750,0.6070,0.000000) (3.8750,0.6115,0.0000) (0.4600,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6115,0.000000) (3.8750,0.6115,0.000000) (3.8750,0.6190,0.0000) (0.4600,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6190,0.000000) (3.8750,0.6190,0.000000) (3.8750,0.6275,0.0000) (0.4600,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6275,0.000000) (3.8750,0.6275,0.000000) (3.8750,0.6390,0.0000) (0.4600,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6390,0.000000) (3.8750,0.6390,0.000000) (3.8750,0.6510,0.0000) (0.4600,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.6510,0.000000) (3.8750,0.6510,0.000000) (3.8750,0.8205,0.0000) (0.4600,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(0.4600,0.8205,0.000000) (3.8750,0.8205,0.000000) (3.8750,0.8710,0.0000) (0.4600,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.3850,0.000000) (3.9850,0.3850,0.000000) (3.9850,0.4460,0.0000) (3.8750,0.4460,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4460,0.000000) (3.9850,0.4460,0.000000) (3.9850,0.4485,0.0000) (3.8750,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4485,0.000000) (3.9850,0.4485,0.000000) (3.9850,0.4555,0.0000) (3.8750,0.4555,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4555,0.000000) (3.9850,0.4555,0.000000) (3.9850,0.4620,0.0000) (3.8750,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4620,0.000000) (3.9850,0.4620,0.000000) (3.9850,0.4705,0.0000) (3.8750,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4705,0.000000) (3.9850,0.4705,0.000000) (3.9850,0.4910,0.0000) (3.8750,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4910,0.000000) (3.9850,0.4910,0.000000) (3.9850,0.4960,0.0000) (3.8750,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.4960,0.000000) (3.9850,0.4960,0.000000) (3.9850,0.5015,0.0000) (3.8750,0.5015,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5015,0.000000) (3.9850,0.5015,0.000000) (3.9850,0.5085,0.0000) (3.8750,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5085,0.000000) (3.9850,0.5085,0.000000) (3.9850,0.5165,0.0000) (3.8750,0.5165,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5165,0.000000) (3.9850,0.5165,0.000000) (3.9850,0.5410,0.0000) (3.8750,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5410,0.000000) (3.9850,0.5410,0.000000) (3.9850,0.5485,0.0000) (3.8750,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5485,0.109718) (3.9850,0.5485,0.109718) (3.9850,0.5775,0.1097) (3.8750,0.5775,0.1097)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.5775,0.000000) (3.9850,0.5775,0.000000) (3.9850,0.6010,0.0000) (3.8750,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6010,0.000000) (3.9850,0.6010,0.000000) (3.9850,0.6070,0.0000) (3.8750,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6070,0.000000) (3.9850,0.6070,0.000000) (3.9850,0.6115,0.0000) (3.8750,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6115,0.000000) (3.9850,0.6115,0.000000) (3.9850,0.6190,0.0000) (3.8750,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6190,0.000000) (3.9850,0.6190,0.000000) (3.9850,0.6275,0.0000) (3.8750,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6275,0.000000) (3.9850,0.6275,0.000000) (3.9850,0.6390,0.0000) (3.8750,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6390,1.704545) (3.9850,0.6390,1.704545) (3.9850,0.6510,1.7045) (3.8750,0.6510,1.7045)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.6510,0.000000) (3.9850,0.6510,0.000000) (3.9850,0.8205,0.0000) (3.8750,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.8750,0.8205,0.000000) (3.9850,0.8205,0.000000) (3.9850,0.8710,0.0000) (3.8750,0.8710,0.0000)};

			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.3850,0.051609) (6.1450,0.3850,0.051609) (6.1450,0.4460,0.0516) (3.9850,0.4460,0.0516)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4460,0.000000) (6.1450,0.4460,0.000000) (6.1450,0.4485,0.0000) (3.9850,0.4485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4485,0.138889) (6.1450,0.4485,0.138889) (6.1450,0.4555,0.1389) (3.9850,0.4555,0.1389)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4555,0.000000) (6.1450,0.4555,0.000000) (6.1450,0.4620,0.0000) (3.9850,0.4620,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4620,0.000000) (6.1450,0.4620,0.000000) (6.1450,0.4705,0.0000) (3.9850,0.4705,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4705,0.000000) (6.1450,0.4705,0.000000) (6.1450,0.4910,0.0000) (3.9850,0.4910,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4910,0.000000) (6.1450,0.4910,0.000000) (6.1450,0.4960,0.0000) (3.9850,0.4960,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.4960,0.079966) (6.1450,0.4960,0.079966) (6.1450,0.5015,0.0800) (3.9850,0.5015,0.0800)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5015,0.000000) (6.1450,0.5015,0.000000) (6.1450,0.5085,0.0000) (3.9850,0.5085,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5085,0.173611) (6.1450,0.5085,0.173611) (6.1450,0.5165,0.1736) (3.9850,0.5165,0.1736)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5165,0.000000) (6.1450,0.5165,0.000000) (6.1450,0.5410,0.0000) (3.9850,0.5410,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5410,0.000000) (6.1450,0.5410,0.000000) (6.1450,0.5485,0.0000) (3.9850,0.5485,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5485,0.000000) (6.1450,0.5485,0.000000) (6.1450,0.5775,0.0000) (3.9850,0.5775,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.5775,0.000000) (6.1450,0.5775,0.000000) (6.1450,0.6010,0.0000) (3.9850,0.6010,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6010,0.000000) (6.1450,0.6010,0.000000) (6.1450,0.6070,0.0000) (3.9850,0.6070,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6070,0.000000) (6.1450,0.6070,0.000000) (6.1450,0.6115,0.0000) (3.9850,0.6115,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6115,0.000000) (6.1450,0.6115,0.000000) (6.1450,0.6190,0.0000) (3.9850,0.6190,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6190,0.000000) (6.1450,0.6190,0.000000) (6.1450,0.6275,0.0000) (3.9850,0.6275,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6275,0.000000) (6.1450,0.6275,0.000000) (6.1450,0.6390,0.0000) (3.9850,0.6390,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6390,0.000000) (6.1450,0.6390,0.000000) (6.1450,0.6510,0.0000) (3.9850,0.6510,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.6510,0.000000) (6.1450,0.6510,0.000000) (6.1450,0.8205,0.0000) (3.9850,0.8205,0.0000)};
			\addplot3[patch,shader=faceted,patch type=rectangle] coordinates {(3.9850,0.8205,0.000000) (6.1450,0.8205,0.000000) (6.1450,0.8710,0.0000) (3.9850,0.8710,0.0000)};
